---
title: "figures_and_tables"
author: "Emily"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Library packages

```{r}
library(tidyverse)
library(here)
library(gt)
library(Hmisc)
library(corrplot)
library(cowplot)
library(janitor)
library(ggpubr)
library(knitr)
```


#   Load BC data
```{r}
BC <- read.csv(here::here("Brown_fraserblackcarbon_data.csv")) %>%
  clean_names()


loadest <- read.csv(here::here("hopedischarge_loadestflux.csv"))
```



#   Process BC data for Table 1

##    Wide version loadest dataset
```{r}
loadest_wide <- loadest %>%
  select(c(date,
           hope_discharge_m3_s,
           carbon_class,
           AMLE_loadest)) %>%
  group_by(date, carbon_class) %>%
  summarise(hope_discharge_m3_s = mean(hope_discharge_m3_s, na.rm = TRUE),
            AMLE_average = mean(AMLE_loadest, na.rm = TRUE)) %>%
  pivot_wider(id_cols = c(date, hope_discharge_m3_s),
              names_from = carbon_class,
              values_from = AMLE_average) %>%
  rename(dbc_flux_tonnes_day = DBC,
         doc_flux_tonnes_day = DOC,
         pbc_flux_tonnes_day = PBC)

```


##    Selecting columns for correlation matrix
```{r}
cormatdata_incldate <- BC %>%
  filter(site == "Hope") %>%
  left_join(loadest_wide %>% select(date, hope_discharge_m3_s, dbc_flux_tonnes_day, pbc_flux_tonnes_day)) %>%
  select(c(date, 
           dbc_concentration_mg_l, dbc_flux_tonnes_day, dbc_b6ca_b5ca,
           pbc_concentration_mg_l, pbc_flux_tonnes_day, pbc_b6ca_b5ca,
           hope_discharge_m3_s, doc_concentration_mg_l)) %>%
  mutate(year = year(date), 
         month = month(date)) %>%
  select(year, month, everything()) %>%
  select(-date)

```



#   Load and process environmental data for Table 1

##    SWE
```{r}
#Identifying station ID's within the watershed of the Fraser River at Hope
stations <- read.csv(here::here("SNW_ASWS_BC08MF0001watershed.csv"))%>%
  mutate(TYPE = "Automatic") %>%
  filter(STATUS == "Active") %>%
  select(c(LCTN_ID)) %>%
  pull()


#Current season data
SWE_current_raw <- read.csv(here::here("SWDaily.csv")) 

SWE_current <- SWE_current_raw %>%
  mutate(Date = as.Date(DATE.UTC.)) %>%
  select(Date, 2:111) %>%
  rename_with(.fn = \(x)sub("X","",x)) %>%
  rename_with(.fn = \(x)str_extract(x, pattern = "[^.]+")) %>%
  aggregate(.~Date, 
            FUN = mean,
            na.rm = TRUE, na.action = NULL) %>%
  mutate_at(2:110, function(x) ifelse(is.nan(x), NA, x)) %>%
  filter(Date <= '2024-02-29')


#Archive data
SWE_archive_raw <- read.csv(here::here("SW_DailyArchive.csv")) 

SWE_archive <- SWE_archive_raw %>%
  mutate(Date = as.Date(DATE.UTC.)) %>%
  select(Date, 2:111) %>%
  rename_with(.fn = \(x)sub("X","",x)) %>%
  rename_with(.fn = \(x)str_extract(x, pattern = "[^.]+")) %>%
  aggregate(.~Date, 
            FUN = mean,
            na.rm = TRUE, na.action = NULL) %>%
  mutate_at(2:110, function(x) ifelse(is.nan(x), NA, x)) %>%
  filter(Date >= '2023-02-01')


#Combining current season and archive data, and select only stations within the watershed of the Fraser River at Hope
SWE_daily <- full_join(SWE_archive, SWE_current) %>%
  pivot_longer(cols = 2:121,
               names_to = "station",
               values_to = "SWE_mm") %>%
  filter(station %in% stations)


#Summarize by month
SWE_monthly <- SWE_daily %>%
  group_by(year(Date), month(Date)) %>%
  summarise(SWE_avg_mm = mean(SWE_mm, na.rm = TRUE)) %>%
  rename("year" = "year(Date)",
         "month" = "month(Date)") %>%
    mutate_all(function(x) ifelse(is.nan(x), NA, x))


#Calculate monthly change 
SWE_monthly_change <- SWE_monthly %>%
  ungroup() %>%
  arrange(year, month) %>%
  mutate(SWE_diff_mm = SWE_avg_mm - lag(SWE_avg_mm)) %>%
  filter(!(year == "2023" & month == "2"))


#Only keeping negative values for snowmelt
SWE_melt_monthly <- SWE_monthly_change %>%
  mutate(SWE_melt_mm = ifelse(SWE_diff_mm < 0,
                              -SWE_diff_mm,
                              0))
```


##    Burned area
```{r}
fire_archive_raw <- read.csv(here::here("fire_perimeters_2023.csv"))
fire_current_raw <- read.csv(here::here("fire_perimeters_2024.csv"))

fire_raw <- full_join(fire_archive_raw, fire_current_raw)

fire_monthly <- fire_raw %>%
  select(FIRE_DATE, AREA_SQM) %>%
  mutate(FIRE_DATE = ymd(FIRE_DATE)) %>%
  filter(FIRE_DATE >= '2023-03-01' & FIRE_DATE <= '2024-02-28') %>%
  mutate(year = year(FIRE_DATE),
         month = month(FIRE_DATE)) %>%
  select(-FIRE_DATE) %>%
  group_by(year, month) %>%
  summarise(burned_area_m2 = sum(AREA_SQM))
```


#    Table 1: Correlation matrix

##   Join datasets
```{r}
cormatdata_incldate <- cormatdata_incldate %>%
  left_join(SWE_melt_monthly) %>%
  select(-SWE_avg_mm, -SWE_diff_mm)

cormatdata_incldate <- cormatdata_incldate %>%
  left_join(fire_monthly) %>%
  mutate(burned_area_m2 = replace_na(burned_area_m2, 0))

cormatdata <- cormatdata_incldate %>%
  select(-month, -year) %>%
  mutate_all(~as.numeric(.))
```



##   Run correlation matrix
```{r}

# Calculate correlation matrix
res <- rcorr(as.matrix(cormatdata))

# Extract correlation coefficients (complete table, presented in supporting information)
resr <- res$r

# Select columns and rows for table 1
resr_table1 <- res$r[c(7:10) , c(1:6)]

# Extract p-values (complete table, presented in supporting information)
resp <- res$P

# Select columns and rows for table 1
resp_table1 <- res$P[c(7:10) , c(1:6)]


```


##  Format tibble for cor coefficients (res) and p values (res2p)
```{r}
cortable <- resr_table1 %>%
  as_tibble(rownames = NA) %>%
  rownames_to_column() %>%
  rename_with(~paste0(.x, "_corcoef"), -rowname)

cortable_p <- resp_table1 %>%
  as_tibble(rownames = NA) %>%
  rownames_to_column() %>%
  rename_with(~paste0(.x, "_p"), -rowname)

cortable <- left_join(cortable, cortable_p)

#Round correlation coefficient values
cortable <- cortable %>%
  mutate_at(c(2:10), ~round(.x, digits = 3))


#Adding significance stars
cortable <- cortable %>%
  mutate(dbc_concentration_mg_l_corcoef = ifelse(dbc_concentration_mg_l_p <= 0.001,
                                     paste0(dbc_concentration_mg_l_corcoef, "***"),
                                     ifelse(dbc_concentration_mg_l_p <= 0.01,
                                            paste0(dbc_concentration_mg_l_corcoef, "**"),
                                            ifelse(dbc_concentration_mg_l_p<= 0.05,
                                                   paste0(dbc_concentration_mg_l_corcoef, "*"),
                                                   dbc_concentration_mg_l_corcoef))),
                                            
         dbc_flux_tonnes_day_corcoef = ifelse(dbc_flux_tonnes_day_p <= 0.001,
                                              paste0(dbc_flux_tonnes_day_corcoef, "***"),
                                               ifelse(dbc_flux_tonnes_day_p <= 0.01,
                                                      paste0(dbc_flux_tonnes_day_corcoef, "**"),
                                                      ifelse(dbc_flux_tonnes_day_p<= 0.05,
                                                             paste0(dbc_flux_tonnes_day_corcoef, "*"),
                                                             dbc_flux_tonnes_day_corcoef))),
           
         dbc_b6ca_b5ca_corcoef =  ifelse(dbc_b6ca_b5ca_p <= 0.001,
                                              paste0(dbc_b6ca_b5ca_corcoef, "***"),
                                               ifelse(dbc_b6ca_b5ca_p <= 0.01,
                                                      paste0(dbc_b6ca_b5ca_corcoef, "**"),
                                                      ifelse(dbc_b6ca_b5ca_p<= 0.05,
                                                             paste0(dbc_b6ca_b5ca_corcoef, "*"),
                                                             dbc_b6ca_b5ca_corcoef))),
         
         pbc_concentration_mg_l_corcoef = ifelse(pbc_concentration_mg_l_p <= 0.001,
                                     paste0(pbc_concentration_mg_l_corcoef, "***"),
                                     ifelse(pbc_concentration_mg_l_p <= 0.01,
                                            paste0(pbc_concentration_mg_l_corcoef, "**"),
                                            ifelse(pbc_concentration_mg_l_p<= 0.05,
                                                   paste0(pbc_concentration_mg_l_corcoef, "*"),
                                                   pbc_concentration_mg_l_corcoef))),
                                            
         pbc_flux_tonnes_day_corcoef = ifelse(pbc_flux_tonnes_day_p <= 0.001,
                                              paste0(pbc_flux_tonnes_day_corcoef, "***"),
                                               ifelse(pbc_flux_tonnes_day_p <= 0.01,
                                                      paste0(pbc_flux_tonnes_day_corcoef, "**"),
                                                      ifelse(pbc_flux_tonnes_day_p<= 0.05,
                                                             paste0(pbc_flux_tonnes_day_corcoef, "*"),
                                                             pbc_flux_tonnes_day_corcoef))),
           
         pbc_b6ca_b5ca_corcoef =  ifelse(pbc_b6ca_b5ca_p <= 0.001,
                                              paste0(pbc_b6ca_b5ca_corcoef, "***"),
                                               ifelse(pbc_b6ca_b5ca_p <= 0.01,
                                                      paste0(pbc_b6ca_b5ca_corcoef, "**"),
                                                      ifelse(pbc_b6ca_b5ca_p<= 0.05,
                                                             paste0(pbc_b6ca_b5ca_corcoef, "*"),
                                                             pbc_b6ca_b5ca_corcoef)))
         
         
         )
```


##    Select final table
```{r, results = 'asis'}
table1 <- cortable %>%
  select(c(rowname,
           dbc_concentration_mg_l_corcoef,
           dbc_flux_tonnes_day_corcoef,
           dbc_b6ca_b5ca_corcoef,
           pbc_concentration_mg_l_corcoef,
           pbc_flux_tonnes_day_corcoef,
           pbc_b6ca_b5ca_corcoef)) %>%
  rename("DBC concentration (mg/L)" = "dbc_concentration_mg_l_corcoef",
         "DBC flux (tonnes/day)" = "dbc_flux_tonnes_day_corcoef",
         "DBC B6CA:B5CA" = "dbc_b6ca_b5ca_corcoef",
         "PBC concentration (mg/L)" = "pbc_concentration_mg_l_corcoef",
         "PBC flux (tonnes/day)" = "pbc_flux_tonnes_day_corcoef",
         "PBC B6CA:B5CA" = "pbc_b6ca_b5ca_corcoef") %>%
  mutate(rowname = c("River discharge",
                     "DOC concentration",
                     "Snow melt",
                     "Active fire burned area"))
           
kable(table1)
```



#   Figure 2
```{r}
BC_hope <- BC %>%
  filter(site == "Hope") 


BC_hope_summarized_flux <- left_join(BC_hope, 
                                     loadest_wide)

BC_hope_conc_flux <- BC_hope_summarized_flux %>%
  select(date,
         hope_discharge_m3_s,
         dbc_concentration_mg_l,
         pbc_concentration_mg_l,
         dbc_flux_tonnes_day,
         pbc_flux_tonnes_day,
         dbc_b6ca_b5ca,
         pbc_b6ca_b5ca) %>%
  mutate(across(hope_discharge_m3_s:pbc_b6ca_b5ca, ~as.numeric(.))) %>%
  pivot_longer(cols = starts_with(c("dbc", "pbc")),
               names_to = c(".value", "measurement"),
               names_pattern = "(dbc|pbc)_(.*)") %>%
  mutate(date = as.Date(date))

  
```

Load and prep discharge data
```{r}
#Discharge data
Hope_discharge <- loadest %>%
  select(date:hope_discharge_m3_s)

#Date format
Hope_discharge <- Hope_discharge %>%
  mutate(date = as.Date(date))

#Summarizing by day
Hope_discharge_daily <- Hope_discharge %>%
  group_by(date) %>%
  summarise(hope_discharge_m3_s = mean(hope_discharge_m3_s))
```

Join datasets
```{r}
fig2data <- full_join(Hope_discharge_daily, BC_hope_conc_flux)
```

##    Panel a: Concentration
```{r}
rescale_conc <- 8974.525 / 0.58935

BC_hope_conc_plot <-  filter(fig2data, measurement %in% c(NA, "concentration_mg_l")) %>%
  ggplot(aes(x = date)) +
  
  geom_point(data = filter(fig2data, measurement == "concentration_mg_l"),
                aes(y = dbc,
                color = "DBC")) +
  geom_line(data = filter(fig2data, measurement == "concentration_mg_l"),
                aes(y = dbc,
                color = "DBC",
                linetype = "DBC")) +
  
  geom_point(data = filter(fig2data, measurement == "concentration_mg_l"),
                aes(y = pbc,
                color = "PBC")) +
  geom_line(data = filter(fig2data, measurement == "concentration_mg_l"),
                aes(y = pbc,
                color = "PBC",
                linetype = "PBC")) +
  
  geom_line(aes(y = hope_discharge_m3_s / rescale_conc,
                color = "Discharge",
                linetype = "Discharge")) +
  
  theme_classic() +
  scale_x_date(limits = as.Date(c('1/3/2023', '28/2/2024'), format="%d/%m/%Y"),
               date_breaks = "1 month",
               date_labels = "%b %Y") +
  labs(x = NULL) +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "none",
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 14)) +
  scale_color_manual(name = "Legend",
                     breaks = c("DBC",
                                "PBC",
                                "DBC:DOC (%)",
                                "Discharge"),
                     values = c("#1B9E77",
                                "#D95F02",
                                "#7570B3",
                                "#666666")) + 
  scale_linetype_manual(name = "Legend", 
                        breaks = c("DBC",
                                "PBC",
                                "DBC:DOC (%)",
                                "Discharge"),
                        values = c("solid",
                                   "solid",
                                   "solid",
                                   "dashed")) + # Setting line type for Discharge line
  scale_y_continuous(name = expression('Concentration (mg L'^-1*')'),
                labels = scales::comma,
                sec.axis = sec_axis(~.*rescale_conc, name = expression('River discharge (m'^3*'s'^-1*')'),
                                         labels = scales::comma))

```




##    Panel b: Flux 
```{r}
rescale_flux <- 8974.525 / 178

BC_hope_flux_plot <-  filter(fig2data, measurement %in% c(NA, "flux_tonnes_day")) %>%
  ggplot(aes(x = date)) +
  
  geom_point(data = filter(fig2data, measurement == "flux_tonnes_day"),
                aes(y = dbc,
                color = "DBC")) +
  geom_line(data = filter(fig2data, measurement == "flux_tonnes_day"),
                aes(y = dbc,
                color = "DBC",
                linetype = "DBC")) +
  
  geom_point(data = filter(fig2data, measurement == "flux_tonnes_day"),
                aes(y = pbc,
                color = "PBC")) +
  geom_line(data = filter(fig2data, measurement == "flux_tonnes_day"),
                aes(y = pbc,
                color = "PBC",
                linetype = "PBC")) +
  
  geom_line(aes(y = hope_discharge_m3_s / rescale_flux,
                color = "Discharge",
                linetype = "Discharge")) +
  
  theme_classic() +
  scale_x_date(limits = as.Date(c('1/3/2023', '28/2/2024'), format="%d/%m/%Y"),
               date_breaks = "1 month",
               date_labels = "%b %Y") +
  labs(x = NULL) +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "none",
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 14)) +
  scale_color_manual(name = "Legend",
                     breaks = c("DBC",
                                "PBC",
                                "DBC:DOC (%)",
                                "Discharge"),
                     values = c("#1B9E77",
                                "#D95F02",
                                "#7570B3",
                                "#666666")) + 
  scale_linetype_manual(name = "Legend", 
                        breaks = c("DBC",
                                "PBC",
                                "DBC:DOC (%)",
                                "Discharge"),
                        values = c("solid",
                                   "solid",
                                   "solid",
                                   "dashed")) + # Setting line type for Discharge line
  scale_y_continuous(name = expression('Flux (Mg d'^-1*')'),
                labels = scales::comma,
                sec.axis = sec_axis(~.*rescale_flux, name = expression('River discharge (m'^3*'s'^-1*')'),
                                         labels = scales::comma))


```


##    Panel c: DBC B6CA:B5CA

```{r}
# Calculate the rescaling factor
rescale_formula_d <- function(x) { ((84787.54*x) - 30523.51) }
unscale_formula_d <- function(x) { ((x + 30523.51)/84787.54)}

#plot DBC
BC_hope_dbc_bpca_plot <-  filter(fig2data, measurement %in% c(NA, "b6ca_b5ca")) %>% ggplot(aes(x = date)) + 
  geom_point(data = filter(fig2data, measurement == "b6ca_b5ca"),
                aes(y = dbc,
                color = "DBC")) +
  geom_line(data = filter(fig2data, measurement == "b6ca_b5ca"),
                aes(y = dbc,
                color = "DBC",
                linetype = "DBC")) +
  
  geom_line(aes(y = unscale_formula_d(hope_discharge_m3_s), 
                color = "Discharge", 
                linetype = "Discharge")) +
  
  theme_classic() +
  scale_x_date(limits = as.Date(c('1/3/2023', '28/2/2024'), format="%d/%m/%Y"),
               date_breaks = "1 month",
               date_labels = "%b %Y") +
  labs(x = NULL) +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "none",
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 14)) +
  scale_color_manual(name = "Legend",
                     breaks = c("DBC",
                                "PBC",
                                "DBC:DOC (%)",
                                "Discharge"),
                     values = c("#1B9E77",
                                "#D95F02",
                                "#7570B3",
                                "#666666")) + 
  scale_linetype_manual(name = "Legend", 
                        breaks = c("DBC",
                                "PBC",
                                "DBC:DOC (%)",
                                "Discharge"),
                        values = c("solid",
                                   "solid",
                                   "solid",
                                   "dashed")) + # Setting line type for Discharge line
  
  scale_y_continuous(name = "B6CA:B5CA", labels = scales::comma, limits = c(0.36, 0.47),
                     sec.axis = sec_axis(~ rescale_formula_d(.), 
                                         name = expression('River discharge (m'^3*'s'^-1*')', 
                                         labels = scales::comma)))

```



##    Panel d: PBC B6CA:B5CA
```{r}
# Calculate the rescaling factor
rescale_factor_p <- (max(fig2data$hope_discharge_m3_s, na.rm = TRUE))/2.0018000

#plot PBC
BC_hope_pbc_bpca_plot <-  filter(fig2data, measurement %in% c(NA, "b6ca_b5ca")) %>% ggplot(aes(x = date)) + 
  geom_point(data = filter(fig2data, measurement == "b6ca_b5ca"),
                aes(y = pbc,
                color = "PBC")) +
  geom_line(data = filter(fig2data, measurement == "b6ca_b5ca"),
                aes(y = pbc,
                color = "PBC",
                linetype = "PBC")) +

  geom_line(aes(y = hope_discharge_m3_s / rescale_factor_p,
                color = "Discharge",
                linetype = "Discharge")) +  # Rescale discharge values
  
  theme_classic() +
  scale_x_date(limits = as.Date(c('1/3/2023', '28/2/2024'), format="%d/%m/%Y"),
               date_breaks = "1 month",
               date_labels = "%b %Y") +
  labs(x = NULL) +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "none",
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 14)) +
  scale_color_manual(name = "Legend",
                     breaks = c("DBC",
                                "PBC",
                                "DBC:DOC (%)",
                                "Discharge"),
                     values = c("#1B9E77",
                                "#D95F02",
                                "#7570B3",
                                "#666666")) + 
  scale_linetype_manual(name = "Legend", 
                        breaks = c("DBC",
                                "PBC",
                                "DBC:DOC (%)",
                                "Discharge"),
                        values = c("solid",
                                   "solid",
                                   "solid",
                                   "dashed")) + # Setting line type for Discharge line
  
  scale_y_continuous(name = "B6CA:B5CA",
                labels = scales::comma,
                sec.axis = sec_axis(~.*rescale_factor_p, 
                                    name = expression('River discharge (m'^3*'s'^-1*')'),
                                    labels = scales::comma))

```




##    Pabel e: DBC:DOC%

Select DBC:DOC data
```{r}
DBCDOC_hope <- 
  BC %>%
  filter(site == "Hope") %>%
  select(c(date, dbc_concentration_mg_l, doc_concentration_mg_l)) %>%
  mutate(DBC_DOC = (dbc_concentration_mg_l/doc_concentration_mg_l)*100) %>%
  rename("DBC:DOC_%" = "DBC_DOC") %>%
  mutate(date = as.Date(date),
         measurement = "DBC:DOC") %>%
  select(-c(dbc_concentration_mg_l, doc_concentration_mg_l))

DBCDOC_hope <- full_join(Hope_discharge_daily, DBCDOC_hope)

fig2data <- full_join(fig2data, DBCDOC_hope)

```

Plotting:
```{r}

# Calculate the rescaling factor
rescale_DBCDOC <- 8974.525 / 8.75

#Plot DBC:DOC
BC_hope_DBCDOC_plot <-  filter(fig2data, measurement %in% c(NA, "DBC:DOC")) %>% ggplot(aes(x = date)) + 
  geom_point(data = filter(fig2data, measurement == "DBC:DOC"),
                aes(y = `DBC:DOC_%`,
                color = "DBC:DOC (%)")) +
  geom_line(data = filter(fig2data, measurement == "DBC:DOC"),
                aes(y = `DBC:DOC_%`,
                color = "DBC:DOC (%)",
                linetype = "DBC:DOC (%)")) +
  
  geom_line(aes(y = hope_discharge_m3_s / rescale_DBCDOC,
                color = "Discharge",
                linetype = "Discharge")) +
  
  theme_classic() +
  scale_x_date(limits = as.Date(c('1/3/2023', '28/2/2024'), format="%d/%m/%Y"),
               date_breaks = "1 month",
               date_labels = "%b %Y") +
  labs(x = NULL) +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "none",
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 14)) +
  scale_color_manual(name = "Legend",
                     breaks = c("DBC",
                                "PBC",
                                "DBC:DOC (%)",
                                "Discharge"),
                     values = c("#1B9E77",
                                "#D95F02",
                                "#7570B3",
                                "#666666")) + 
  scale_linetype_manual(name = "Legend", 
                        breaks = c("DBC",
                                "PBC",
                                "DBC:DOC (%)",
                                "Discharge"),
                        values = c("solid",
                                   "solid",
                                   "solid",
                                   "dashed")) + # Setting line type for Discharge line
  scale_y_continuous(name = "DBC:DOC (%)",
                labels = scales::comma,
                sec.axis = sec_axis(~.*rescale_DBCDOC, name = expression('River discharge (m'^3*'s'^-1*')'),
                                         labels = scales::comma))

```



##    Panel f: Discharge only
```{r}
discharge_plot <-  filter(fig2data, is.na(measurement) == TRUE) %>% 
  ggplot(aes(x = date)) + 

  geom_line(aes(y = hope_discharge_m3_s,
                color = "Discharge",
                linetype = "Discharge")) +
  
  theme_classic() +
  scale_x_date(limits = as.Date(c('1/3/2023', '28/2/2024'), format="%d/%m/%Y"),
               date_breaks = "1 month",
               date_labels = "%b %Y") +
  labs(x = NULL) +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "none",
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 14)) +
  scale_color_manual(name = "Legend",
                     breaks = c("DBC",
                                "PBC",
                                "DBC:DOC (%)",
                                "Discharge"),
                     values = c("#1B9E77",
                                "#D95F02",
                                "#7570B3",
                                "#666666")) + 
  scale_linetype_manual(name = "Legend", 
                        breaks = c("DBC",
                                "PBC",
                                "DBC:DOC (%)",
                                "Discharge"),
                        values = c("solid",
                                   "solid",
                                   "solid",
                                   "dashed")) + # Setting line type for Discharge line
  scale_y_continuous(name = expression('River discharge (m'^3*'s'^-1*')'),
                labels = scales::comma)

```



##    Legend:
```{r, fig.height = 1, fig.width = 12}
legend_facet <- BC_hope_conc_plot +
    geom_point(data = filter(fig2data, measurement == "DBC:DOC"),
                aes(y = `DBC:DOC_%`,
                color = "DBC:DOC (%)")) +
  geom_line(data = filter(fig2data, measurement == "DBC:DOC"),
                aes(y = `DBC:DOC_%`,
                color = "DBC:DOC (%)",
                linetype = "DBC:DOC (%)")) +
  theme(legend.position = "bottom",
        legend.text = element_text(size = 16),
        legend.title = element_text(size = 20),
        legend.key.size = unit(1, "cm")) 

legend_facet <- get_legend(legend_facet) %>% 
  as_ggplot()

```

##    Combine for final figure
```{r, fig.width= 13, fig.height = 15}
#First align the plots on the left side of the grid
plots <- plot_grid(BC_hope_conc_plot,
                     BC_hope_flux_plot,
                     BC_hope_dbc_bpca_plot,
                     BC_hope_pbc_bpca_plot,
                     BC_hope_DBCDOC_plot,
                     discharge_plot,
                     align="hv", axis="tblr",
                   labels = "auto",
                   label_size = 18,
                   scale = 0.9,
                   ncol = 2)


#add the legend
figure2 <- plot_grid(plots,
                     legend_facet,
                     ncol = 1,
                     rel_heights = c(9, 1))

figure2

```

